\cvsection{Projects}
\begin{cventries}
  \cventry
  {Electrical and Electronic Engineering Introduction}
  {Home Security Alarm}
  {}
  {Apr. 2020 - Jun. 2020}
  {
    \begin{cvitems}
      \item {Introduced to arduino}
      \item {Learn how managing a project, working as a team and making a presentation.}
    \end{cvitems}
  }
\end{cventries}

\begin{cventries}
  \cventry
  {C/C++ Programming Language}
  {Student Management System}
  {}
  {Apr. 2021 - May. 2021}
  {
    \begin{cvitems}
      \item {Build a simple Student Management System}
      \item {Learn about C and C++ programming : pointers, class, variable types,\dots}
    \end{cvitems}
  }
\end{cventries}

\begin{cventries}
  \cventry
  {Data Structures and Algorithms}
  {Bank Management System}
  {}
  {May. 2022 - Jun. 2022}
  {
    \begin{cvitems}
      \item {Build a simple Terminal-based Bank Management System}
      \item {Learn about Data Structures and Algorithms}
    \end{cvitems}
  }
\end{cventries}

\begin{cventries}
  \cventry
  {Digital Design using VHDL}
  {RISC-SPM}
  {}
  {Jan. 2023 - Mar. 2023}
  {
    \begin{cvitems}
      \item {Design a RISC Stored-Program Machine Using Verilog HDL.}
      \item {Gained knowledge about CPU, hardware description language.}
    \end{cvitems}
  }
\end{cventries}

\begin{cventries}
  \cventry
  {Micro Processor}
  {Audio Spectrum Visualizer}
  {}
  {Jan. 2023 - Mar. 2023}
  {
    \begin{cvitems}
      \item {Design a Audio Spectrum Visualizer on a STM32 cortex m3 chip.}
      \item {Gained knowledge about embedded programming, CPU.}
    \end{cvitems}
  }
\end{cventries}

\begin{cventries}
  \cventry
  {Design Project 2}
  {ID card detection using deep learning for eKYC products}
  {}
  {Jan. 2023 - Mar. 2023}
  {
    \begin{cvitems}
      \item {Learned about Android development.}
      \item {Gained knowledge about Image Processing.}
    \end{cvitems}
  }

\end{cventries}

\begin{cventries}
  \cventry
  {Graduation Project}
  {Grammar Error Correction using deep learning web app}
  {}
  {Jan. 2024 - today}
  {
    \begin{cvitems}
      \item {Learning about Natural Language Processing.}
      \item {Gained knowledge about web development}
    \end{cvitems}
  }

\end{cventries}
